### 2014-04-02 ApTranscriptome_TR.Rmd
Functioning(!) analysis that works on `lm` output from each transcript to report max, min temperatures of expression, and expression shape.

The previous section identified the transcripts with thermally-responsive expression. In this section, I determine the shape of the expression response to temperature for each transcript. Categories of expression response are:

@@

response.type <- ldply(interaction.transcripts, .progress = "text", .inform = TRUE, RxNtype)

# plot
#qplot(val, pTPM, facets = .~colony, data = A22.pout, geom="smooth")

>>>>

The previous section identified the transcripts with thermally-responsive expression. In this section, I determine the shape of the expression response to temperature for each transcript. Catego
ries of expression response are:

@@

interaction.response.type <- ldply(interaction.transcripts, .progress = "text", .inform = TRUE, RxNtype)

test.transcripts <- interaction.transcripts[1000:1009]
response.type <- ldply(test.transcripts, .progress = "text", .inform = TRUE, RxNtype)

# plot
qplot(val, pTPM, facets = .~colony, data = Ar.pout, geom="smooth")
qplot(val, pTPM, facets = .~colony, data = pout, geom="smooth")

qplot(val, pTPM, facets = .~colony, data = Ar.pout, geom="smooth")
